Differential invariant signatures for planar Lie group transformations of images

### 2019-09-03 paper/newpaper.tex
Included affine invariants in table

\documentclass[review,onefignum,onetabnum]{siamonline190516}
\usepackage{amsmath,amsfonts,graphicx}
\def\R{\mathbb{R}}
\usepackage{xcolor}
\usepackage{todonotes}
\usepackage{tikz}

@@

\begin{tabular}{cccc}
\centering
Degree & Weight & Diagram & Invariant \\
\hline
2 & 2 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $fxx$ \\

2 & 2 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture}
& $fxx$ \\

3 & 3 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (3);
\end{tikzpicture}
& $fxx$ \\

3 & 4 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (3);
    \draw[-] (2) to (3);
\end{tikzpicture}
& $fxx$ \\

%=====
3 & 3 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
\end{tikzpicture}
& $fxx$ \\

3 & 4 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to [out=-120,in=120] (2);
    \draw[-] (1) to [out=-60,in=60] (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
\end{tikzpicture}
& $fxx$ \\

2 & 4 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (1);
\end{tikzpicture}
& $fxx$ \\

3 & 4 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to [out=-120,in=120] (2);
    \draw[-] (1) to [out=-60,in=60] (2);
    \draw[-] (2) to (3);
    \draw[-] (1) to (4);
\end{tikzpicture}
& $fxx$ \\

% =========
2 & 4 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $fxx$ \\

3 & 4 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $fxx$ \\

4 & 4 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (1) to (5);
\end{tikzpicture}
& $fxx$ \\
\end{tabular}

@@

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/SE2Transform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/SE2Transform_signature.png}
\caption{A sample $SE(2)$ Transform and 3D signature.}
\label{fig:SE2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/E2Transform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/E2Transform_signature.png}
\caption{A sample $E(2)$ Transform and 3D signature.}
\label{fig:E2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/SA2Transform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/SA2Transform_signature.png}
\caption{A sample $SA(2)$ Transform and 3D signature.}
\label{fig:SA2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/A2Transform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/A2Transform_signature.png}
\caption{A sample $A(2)$ Transform and 3D signature.}
\label{fig:A2}
\end{figure}

@@

The prolonged action is:
\begin{equation}
\small
\arraycolsep=1.4pt
\left(
\begin{array}{c}
  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
 \end{array}
 \right)
 = 
\left(
\begin{array}{ccccccccc}
 a & b & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 -b & a & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 2\mu & -2 \rho & a^2 & 2 a b & b^2 & 0 & 0 & 0 & 0 \\
 2 \rho & 2\mu & -a b & a^2\!-b^2 & a b & 0 & 0 & 0 & 0 \\
 -2\mu & 2 \rho & b^2 & -2 a b & a^2 & 0 & 0 & 0 & 0 \\
 -6 (2 b c d+a \lambda) & 6 (2 a c d-b\lambda) & 6 a \mu &
  M_{64}  & -6 b \rho & a^3 & 3 a^2 b & 3 a b^2 & b^3 \\
 -6 (2 a c d-b\lambda) & -6 (2 b c d+a \lambda) & M_{73}& M_{74} & 
 M_{75} & -a^2 b & a^3\!-2 a b^2 & 2
   a^2 b\!-b^3 & a b^2 \\
 6 (2 b c d+a \lambda) & -6 (2 a c d-b\lambda) & M_{83} & M_{84} & M_{85} & a b^2 & b^3\!-2
   a^2 b & a^3\!-2 a b^2 & a^2 b \\
 6 (2 a c d-b\lambda) & 6 (2 b c d+a \lambda) & 6 b \mu & 
  M_{94} & 6 a \rho & -b^3 & 3 a b^2 & -3 a^2 b & a^3 \\
\end{array}
\right)\left(
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
 \end{array}
 \right).
\label{eqn:mobius}
 \end{equation}
 where
 \begin{equation*}
 \small
 \begin{array}{lll}
M_{64}=-12abc+6d(a^2-b^2), & 
M_{73}=4 d a^2+6 b c a-2 b^2 d, & 
M_{74}=-6 c a^2+12 b d a+6 b^2 c, \\
 M_{75}=-2 d a^2-6 b c a+4 b^2 d, &
 M_{83}=2 c a^2-6 b d a-4 b^2 c, &
 M_{84}=6 (d a^2+2 b c a-b^2 d),\\
 M_{85}=-4 c a^2+6 b d a+2 b^2 c,& 
 M_{94}= -12a b d + 6c(a^2-b^2),\\
\lambda=d^2-c^2, & 
\mu = b d - a c, & 
\rho = b c + a d.
\end{array}
\end{equation*}

@@

\item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \barf_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
rational functions with numerators of degree 6 and denominators $(f_i f_i)^4$, and are relative invariants of weight 8.
\end{enumerate}

@@

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/MobiusTransform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/MobiusTransform_signature.png}
\caption{A sample M\"obius Transform and 3D signature.}
\label{fig:mobius}
\end{figure}

@@

The prolonged action is:
\begin{equation}
\tiny
\arraycolsep=1.4pt
\label{eq:prolong}
\left(
\begin{array}{c}
  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
 \end{array}
 \right)
 = 
\left(
\begin{array}{ccccccccc}
 a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 -2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
 -b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
 -2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
 6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
 2 g (b g+2 a h) & 2 g (d g+2 c h) & -2 a (2 b g+a h) & -4 (b c g+a d g+a c h) & -2 c (2 d
   g+c h) & a^2 b & a (2 b c+a d) & c (b c+2 a d) & c^2 d \\
 2 h (2 b g+a h) & 2 h (2 d g+c h) & -2 b (b g+2 a h) & -4 (b d g+b c h+a d h) & -2 d (d g+2
   c h) & a b^2 & b (b c+2 a d) & d (2 b c+a d) & c d^2 \\
 6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
\end{array}
\right)\left(
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
 \end{array}
 \right).
 \end{equation}

@@

The components of $J$ are polynomials of degree 16, 24, and 8, respectively, and are extremely complicated when written out explicitly. More seriously, $J$ vanishes on generic images. This can be seen as follows. 
Recall the $SA(2)$ invariant $E$ defined in (\ref{eq:E}).
%Let
%$$ E := f_{222}f_1^3 - 3 f_{122}f_1 f_2^2 + 3 f_{112}f_1^2 f_2 - f_{111}f_2^3$$
Then the components of $J$ have the structure
$$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5$$
where the $P_n$ are polynomials of degree $n$. Therefore $J=0$ when $D=E=0$, which 
is a codimension 0 phenomenon for images. In particular, $D=E=0$ at critical points.

@@

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/PSL3RTransform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/PSL3RTransform_signature.png}
\caption{A sample $PSL(3,\mathbb{R})$ Transform and 3D signature.}
\label{fig:PSL3R}
\end{figure}

\section{Extension to larger groups, role of colour, etc.}

@@

\noindent where $\angle(u, v)$ denotes the angle between tangent vectors $u$ and $v$ based at $x \in \mathbb{R}^2$, $\phi \in \Diff$ and $D$ represents the Jacobian. The group is infinite-dimensional, but still small enough that images have local differential invariants.

>>>>

\documentclass[review,onefignum,onetabnum]{siamonline190516}
\usepackage{amsmath,amsfonts,graphicx}
\def\R{\mathbb{R}}
\usepackage{xcolor}
\usepackage{todonotes}
\usepackage{tikz}
\usepackage{array}

@@

\begin{tabular}{cm{1cm}cm{10cm}}
\centering
Degree & Weight & Diagram & Invariant \\
\hline
2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\

2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture}
& $\left(f_{x}\right)^{2} f_{yy} - 2 f_{x} f_{y} f_{xy} + f_{xx}
\left(f_{y}\right)^{2}$ \\

3 & 3 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (3);
\end{tikzpicture}
& $- f_{x} f_{xx} f_{yyy} - f_{x} f_{yy} f_{xxy} + 2 f_{x} f_{xy} f_{xyy} +
f_{xx} f_{y} f_{xyy} + f_{xxx} f_{y} f_{yy} - 2 f_{y} f_{xy} f_{xxy}$ \\

3 & 3 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yyy} + 3 \left(f_{x}\right)^{2} f_{y} f_{xyy} - 3 f_{x} \left(f_{y}\right)^{2} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3}$  \\

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (3);
    \draw[-] (2) to (3);
\end{tikzpicture}
& $2 f_{xx} f_{yyy} f_{xxy} - 2 f_{xx} \left(f_{xyy}\right)^{2} + 2 f_{xxx}
f_{yy} f_{xyy} - 2 f_{xxx} f_{yyy} f_{xy} - 2 f_{yy}
\left(f_{xxy}\right)^{2} + 2 f_{xy} f_{xyy} f_{xxy}$ \\

%=====

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to [out=-120,in=120] (2);
    \draw[-] (1) to [out=-60,in=60] (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
\end{tikzpicture}
& $- f_{x} f_{xx} f_{yy} f_{xyy} + f_{x} f_{xx} f_{yyy} f_{xy} - f_{x} f_{xxx} \left(f_{yy}\right)^{2} + 3 f_{x} f_{yy} f_{xy} f_{xxy} - 2 f_{x} \left(f_{xy}\right)^{2} f_{xyy} - \left(f_{xx}\right)^{2} f_{y} f_{yyy} - f_{xx} f_{y} f_{yy} f_{xxy} + 3 f_{xx} f_{y} f_{xy} f_{xyy} + f_{xxx} f_{y} f_{yy} f_{xy} - 2 f_{y} \left(f_{xy}\right)^{2} f_{xxy}$ \\

2 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (1);
\end{tikzpicture}
& $2 \left(f_{xx}\right)^{2} \left(f_{yy}\right)^{2} - 4 f_{xx} f_{yy} \left(f_{xy}\right)^{2} + 2 \left(f_{xy}\right)^{4}$ \\

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
    \draw[-] (1) to [out=-120,in=120] (2);
    \draw[-] (1) to [out=-60,in=60] (2);
    \draw[-] (2) to (3);
    \draw[-] (1) to (4);
\end{tikzpicture}
& $2 \left(f_{x}\right)^{2} f_{yyy} f_{xxy} - 2 \left(f_{x}\right)^{2} \left(f_{xyy}\right)^{2} - 2 f_{x} f_{xxx} f_{y} f_{yyy} + 2 f_{x} f_{y} f_{xyy} f_{xxy} + 2 f_{xxx} \left(f_{y}\right)^{2} f_{xyy} - 2 \left(f_{y}\right)^{2} \left(f_{xxy}\right)^{2}$ \\

% =========
2 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (1) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\
\end{tabular}

@@

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
\caption{A sample $SE(2)$ Transform and 3D signature.}
\label{fig:SE2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_E2.png}
\includegraphics[width=.45\textwidth]{Figs/E2_signature.png}
\caption{A sample $E(2)$ Transform and 3D signature.}
\label{fig:E2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_SA2.png}
\includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
\caption{A sample $SA(2)$ Transform and 3D signature.}
\label{fig:SA2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_A2.png}
\includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
\caption{A sample $A(2)$ Transform and 3D signature.}
\label{fig:A2}
\end{figure}

@@

The prolonged action is:
\begin{equation}
\arraycolsep=1.4pt
\left(
\begin{array}{c}
  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
 \end{array}
 \right)
 = 
\left(
\begin{array}{ccccccccc}
 a & b & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 -b & a & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 2\mu & -2 \rho & a^2 & 2 a b & b^2 & 0 & 0 & 0 & 0 \\
 2 \rho & 2\mu & -a b & a^2\!-b^2 & a b & 0 & 0 & 0 & 0 \\
 -2\mu & 2 \rho & b^2 & -2 a b & a^2 & 0 & 0 & 0 & 0 \\
 -6 (2 b c d+a \lambda) & 6 (2 a c d-b\lambda) & 6 a \mu &
  M_{64}  & -6 b \rho & a^3 & 3 a^2 b & 3 a b^2 & b^3 \\
 -6 (2 a c d-b\lambda) & -6 (2 b c d+a \lambda) & M_{73}& M_{74} & 
 M_{75} & -a^2 b & a^3\!-2 a b^2 & 2
   a^2 b\!-b^3 & a b^2 \\
 6 (2 b c d+a \lambda) & -6 (2 a c d-b\lambda) & M_{83} & M_{84} & M_{85} & a b^2 & b^3\!-2
   a^2 b & a^3\!-2 a b^2 & a^2 b \\
 6 (2 a c d-b\lambda) & 6 (2 b c d+a \lambda) & 6 b \mu & 
  M_{94} & 6 a \rho & -b^3 & 3 a b^2 & -3 a^2 b & a^3 \\
\end{array}
\right)\left(
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
 \end{array}
 \right).
\label{eqn:mobius}
 \end{equation}
 where
 \begin{equation*}
 \begin{array}{lll}
M_{64}=-12abc+6d(a^2-b^2), & 
M_{73}=4 d a^2+6 b c a-2 b^2 d, & 
M_{74}=-6 c a^2+12 b d a+6 b^2 c, \\
 M_{75}=-2 d a^2-6 b c a+4 b^2 d, &
 M_{83}=2 c a^2-6 b d a-4 b^2 c, &
 M_{84}=6 (d a^2+2 b c a-b^2 d),\\
 M_{85}=-4 c a^2+6 b d a+2 b^2 c,& 
 M_{94}= -12a b d + 6c(a^2-b^2),\\
\lambda=d^2-c^2, & 
\mu = b d - a c, & 
\rho = b c + a d.
\end{array}
\end{equation*}

@@

\item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \bar f_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
rational functions with numerators of degree 6 and denominators $(f_i f_i)^4$, and are relative invariants of weight 8.
\end{enumerate}

@@

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_Mobius.png}
\includegraphics[width=.45\textwidth]{Figs/Mobius_signature.png}
\caption{A sample M\"obius Transform and 3D signature.}
\label{fig:mobius}
\end{figure}

@@

The prolonged action is:
\begin{equation}
\arraycolsep=1.4pt
\label{eq:prolong}
\left(
\begin{array}{c}
  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
 \end{array}
 \right)
 = 
\left(
\begin{array}{ccccccccc}
 a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 -2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
 -b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
 -2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
 6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
 2 g (b g+2 a h) & 2 g (d g+2 c h) & -2 a (2 b g+a h) & -4 (b c g+a d g+a c h) & -2 c (2 d
   g+c h) & a^2 b & a (2 b c+a d) & c (b c+2 a d) & c^2 d \\
 2 h (2 b g+a h) & 2 h (2 d g+c h) & -2 b (b g+2 a h) & -4 (b d g+b c h+a d h) & -2 d (d g+2
   c h) & a b^2 & b (b c+2 a d) & d (2 b c+a d) & c d^2 \\
 6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
\end{array}
\right)\left(
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
 \end{array}
 \right).
 \end{equation}

@@

The components of $J$ are polynomials of degree 16, 24, and 8, respectively, and are extremely complicated when written out explicitly. More seriously, $J$ vanishes on generic images. This can be seen as follows. 
Recall the $SA(2)$ invariant $E$ defined in \todo[inline]{somewhere}

%Let
%$$ E := f_{222}f_1^3 - 3 f_{122}f_1 f_2^2 + 3 f_{112}f_1^2 f_2 - f_{111}f_2^3$$
Then the components of $J$ have the structure
$$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5$$
where the $P_n$ are polynomials of degree $n$. Therefore $J=0$ when $D=E=0$, which 
is a codimension 0 phenomenon for images. In particular, $D=E=0$ at critical points.

@@

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_PSL3R.png}
\includegraphics[width=.45\textwidth]{Figs/PSL3R_signature.png}
\caption{A sample $PSL(3,\mathbb{R})$ Transform and 3D signature.}
\label{fig:PSL3R}
\end{figure}

\section{Extension to larger groups, role of colour, etc.}
\label{sec:aaah}

@@

\noindent where $\angle(u, v)$ denotes the angle between tangent vectors
$u$ and $v$ based at $x \in \mathbb{R}^2$, $\phi \in \textrm{Diff}$ and $D$
represents the Jacobian. The group is infinite-dimensional, but still small
enough that images have local differential invariants.
